When does vapor pressure deficit drive or reduce evapotranspiration?

### 2018-02-16 doc/paper/vpd_et_paper.tex
starting conversion to glboal chagne biology
added gcb

\journalname{Agricultural and Forest Meteorology}

@@

Vapor pressure deficit (VPD) is expected to rise over continents in the future due to the combination of increased temperature and relative humidity drying \citep{Byrne_2013}. Increases in VPD increases the atmospheric demand of evapotranspiration (ET) \citep{Monteith_1965} but also stresses plant stomata \citep{Leuning_1990, MEDLYN_2011}.

>>>>

\journalname{Global Change Biology}

@@

Vapor pressure deficit (VPD) is expected to rise over continents in the future due to the combination of increased temperature and relative humidity drying ** RH drying \citep{Byrne_2013 }. Increases in VPD increases the atmospheric demand of evapotranspiration (ET) \citep{Monteith_1965} but also stresses plant stomata \citep{Leuning_1990, MEDLYN_2011}.
